---
title: "project mkdwn"
output: html_document
date: "2024-05-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminary Data Loading and Cleaning/Filtering to get desired text area from file

### Removing metadata

```{r metadata}
text.v <- scan("cybersecurity2023legislation.txt", what="character", sep="\n")
start.v <- which(text.v == "Alabama")
end.v <- which(text.v == "Establishes the Cyber Maryland Program in the Maryland Technology Development Corporation to increase the cybersecurity workforce in the state, build an advanced cybersecurity workforce, and carry out other purposes related to the cybersecurity workforce in the state; establishes the Cyber Maryland Fund; establishes the Cyber Maryland Board; requires the Maryland Higher Education Commission, in consultation with a certain organization, to expand the Cyber Warrior Diversity Program.")
start.metadata.v <- text.v[1:(start.v - 1)]
end.metadata.v <- text.v[(end.v+1):length(text.v)]
metadata.v <- c(start.metadata.v, end.metadata.v)
laws.v <- text.v[start.v:end.v]
laws.v <- laws.v[!grepl("^[A-Z]+ \\d+$", laws.v)] # removes the H 132
```

## Sorting each of the laws into the keywords

```{r keyword}
keywords <- c("Pending", "Enacted", "Vetoed", "Failed", "Adopted")  # Add more keywords if needed

status_lists <- list() # initialize blocks list

laws_by_state_status <- list() # initialize state list

# Initialize empty lists for each status
for (keyword in keywords) {
  status_lists[keyword] <- list()
}

for (i in 3:length(text.v)) {
  state <- text.v[i - 3] #ALASKA -- LINE 0
  number <- text.v[i - 2] # H 132 -- LINE 1
  title <- text.v[i - 1] # Elections Ballot Security -- LINE 2
  status <- text.v[i] # Pending - Carryover -- LINE 3
  summary <- text.v[i + 1] # Relates to election security, voting and ballots -- LINE 4
  
  # Check if the line contains a status indicator
  if (grepl("Pending", status)) {
    status_line <- paste(title, summary, sep = " ") #if you need to add more lines add them here
#    status_lists[["Pending"]][[length(status_lists[[current_status]]) + 1]] <- status_line
    laws_by_state_status[[state]][["Pending"]] <- c(laws_by_state_status[[state]][["Pending"]], status_line)
  }
   if (grepl("Failed", status)) {
     status_line <- paste(title, summary, sep = " ") #if you need to add more lines add them here
  #   status_lists[["Failed"]][[length(status_lists[[current_status]]) + 1]] <- status_line
     laws_by_state_status[[state]][["Failed"]] <- c(laws_by_state_status[[state]][["Failed"]], status_line)
   }
   if (grepl("Enacted", status)) {
     status_line <- paste(title, summary, sep = " - ") #concatenates items and seperates them with a " - "
#     status_lists[["Enacted"]][[length(status_lists[["Enacted"]]) + 1]] <- status_line
     laws_by_state_status[[state]][["Enacted"]] <- c(laws_by_state_status[[state]][["Enacted"]], status_line)
   }
   if (grepl("Vetoed", status)) {
     status_line <- paste(title, summary, sep = " ") #if you need to add more lines add them here
  #   status_lists[["Vetoed"]][[length(status_lists[[current_status]]) + 1]] <- status_line
     laws_by_state_status[[state]][["Vetoed"]] <- c(laws_by_state_status[[state]][["Vetoed"]], status_line)
   }
   if (grepl("Adopted", status)) {
     status_line <- paste(title, summary, sep = " ") #if you need to add more lines add them here
  #   status_lists[["Adopted"]][[length(status_lists[[current_status]]) + 1]] <- status_line
     laws_by_state_status[[state]][["Adopted"]] <- c(laws_by_state_status[[state]][["Adopted"]], status_line)
   }
}
```


## Print the descriptions sorted by keyword by state

 Example Output:

 State: West Virginia 

 Status: Enacted - Count: 1 \n
 "---------------"\n
 Funding and Requirements for Federal Elections - Relates to the expenditure of federal appropriations from Congress to the secretary of state for purposes that further the administration of federal elections held in the state, payable from the County Assistance Voting Equipment Fund; clarifies the uniform statewide deadline for electronically submitted voter registration applications; changes the deadline by which county clerks must report voter participation history after an election into the statewide voter registration system. 


```{r sort}
 for (state in names(laws_by_state_status)) {
   cat("\n", "\n", "State:", state, "\n", "\n")
   for (status in names(laws_by_state_status[[state]])) {
     cat("\n", "Status:", status, "- Count:", length(laws_by_state_status[[state]][[status]]), "\n")
     for (law_text in laws_by_state_status[[state]][[status]]) {
       cat("---------------\n")
       cat(law_text, "\n")
     }
   }
 }
```


# TESTING GOING THROUGH ALL TF -- WORKS

```{r tf-test}

 for (state in names(laws_by_state_status)) {
   cat("\n", "\n", "State TF-IDF:", state, "\n", "\n")
   for (status in names(laws_by_state_status[[state]])) {
     cat("\n", "Status:", status, "- Count:", length(laws_by_state_status[[state]][[status]]), "\n") #RIGHT
     
#      cat("\n", "\n", "The combined text", "\n", "\n") # remove this line before submitting file
     
 #    for (law_text in laws_by_state_status[[state]][[status]]) {
       law_text = sapply(laws_by_state_status[[state]][[status]], paste, collapse = "\n")
#       cat(law_text, "\n", "\n")
          tryCatch({
     law_text.lower.v <- tolower(law_text)
     law_text.words.l <- strsplit(law_text.lower.v, "\\W")
     law_text.word.v <- unlist(law_text.words.l)
     
     not.blanks.v  <-  which(law_text.word.v!="")
     law_text.word.v <-  law_text.word.v[not.blanks.v]
     law_text.freqs.t <- table(law_text.word.v)
     
     law_text.status.freqs.t <- sort(law_text.freqs.t , decreasing=TRUE)
     law_text.status.rel.freqs.t <- 100*(law_text.status.freqs.t/sum(law_text.status.freqs.t))
     
     # Extract the 10 lowest frequency terms
     low_terms <- tail(names(law_text.status.rel.freqs.t[order(law_text.status.rel.freqs.t)]), 20)
     low_terms_names <- names(law_text.status.rel.freqs.t)[tail(order(law_text.status.rel.freqs.t), 20)]
     low_terms_freqs <- law_text.status.rel.freqs.t[low_terms]
     
     
     #DataFrame for low terms
     
     low_terms_df <- data.frame(Frequency = low_terms_freqs)
    cat("\nLow Frequency Terms:\n")
      print(low_terms_df)
     
     #Output of low term and frequency
     
     cat("\n", "low_terms_names: ", low_terms_names, "\n")
     cat("low_terms_freqs: ", low_terms_freqs, "\n", "\n")
     
     # Extract the 10 highest frequency terms
     high_terms <- head(names(law_text.status.rel.freqs.t[order(law_text.status.rel.freqs.t)]), 20)
     high_terms_names <- names(law_text.status.rel.freqs.t)[head(order(law_text.status.rel.freqs.t), 20)]
     high_terms_freqs <- law_text.status.rel.freqs.t[high_terms]
     
     #Output of high term and frequency
     
     cat("high_terms_names: ", high_terms_names, "\n")
     cat("high_terms_freqs: ", high_terms_freqs, "\n", "\n")
     
   }, error = function(e) {
     cat("\n", "Skipping block due to error:", conditionMessage(e), "\n")
   })
 #    }
   }
 }
```